`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-17 inst/manuscript/manuscript.rmd
Major progress on data flow section (from package documentation);

#Input Data and Data Processing
To analyse raw data stemming from dithionite scramblase assays, `flippant` 
requires for each data point information as the path to the 
fluorometer-generated spectrum, the amount of protein used to reconstitute 
proteoliposomes, the volume used in the assay before and after addition of 
dithionite (to calculate a volume correction factor), the amount of lips 
present (to calculate a proteine to phospholipid ratio or PPR) etc. The 
following function generates a spreadsheet program-compatible tab-delimited 
#Main Features
##Template Generation for Data Input
The following function generates a spreadsheet program-compatible tab-delimited 
`ASCII` template including column names, commentary, expected data type and the 
default used when ommited, supporting the user in providing the data needed.
```{r, code=formatR::usage('scramblaseAssayInputTemplate'), eval=FALSE}
```
The application agnostic tab-delimited format must be maintained for the 
completed table, which is subjected to extensive input checks when read by 
`flippant`.

Spectral input data is read by `flippant` using the information provided in the
input template raw spectra produced by QuantaMaster fluorometer instruments 
(Photon Technology International,Inc., Edison, New Jersey) running software 
versions FelixGX v4.1 and Felix32 v1.20, respectively, as well as simple generic
tab-delimited spectrum representing file format with time (s) and fluorescence 
intensity containing columns are currently supported. File type determination is
handled algorythmically.

>>>>

#Input Data and Data Processing
To analyse raw data stemming from dithionite scramblase assays, `flippant` 
requires for each data point information as the path to the 
fluorometer-generated spectrum, the amount of protein used to reconstitute 
proteoliposomes, the volume used in the assay before and after addition of 
dithionite (to calculate a volume correction factor), the amount of lipids 
present (to calculate a protein to phospholipid ratio or PPR) etc. The user 
supplies this information in one row of a spreadsheet (see below for supporting functionality).

Spectral input data is read by `flippant` using the information provided in the
input template. Raw spectra produced by QuantaMaster fluorometer instruments 
(Photon Technology International, Inc., Edison, New Jersey) running software 
versions FelixGX v4.1 and Felix32 v1.20, respectively, as well as a simple 
generic tab-delimited spectrum representing file format with time (s) and 
fluorescence intensity representing columns are currently supported. 
File type determination is handled algorythmically.

Based on @menon_opsin_2011 and @goren_constitutive_2014, <CHECK THAT THERE'S INFO IN THE LATTER> data is processed as 
follows. Input is format checked and defaults are injected for facultative 
parameters/columns as appropriate. Fluorescence spectra are parsed, including 
determination of when dithionite was added to the sample using `wmtsa`-supplied
methodology <CITE AND MORE DETAIL> and resetting the acquisition time 
accordingly. The zero time point henceforth corresponds to the time of addition. 
Pre-dithionite-addition baseline fluorescence $F_{\text{baseline}}$ is 
determined for each spectrum by averaging (median) over the ten values preceding
dithionite addition. Post-dithinonite-addition minimum fluorescence 
$F_{\text{min}}$ is analogously calculated from the last ten datapoints after 
the default 400 s or the timepoint of measurement supplied by the user in the 
parameter file. $F_{\text{min}}$ is volume-corrected based on supplied reaction 
volumes
with and without dithionite and for each spectrum/datapoint a fluorescence 
reduction is calculated as follows:
$$
y_{\text{raw}} = 1 - \frac{F_{\text{min}}}{F_{\text{baseline}}}
$$
<!--
Data are split for parallel treatment using a combined Experimental Series/Experiment identifier (see above).

A Relative Fluorescence Reduction is calculated in comparison to the liposomes-only/no-protein control).

A Protein per Phospholipid (mg/mmol) ratio (PPR) is calculated.

A probability for a liposome holding ≤ 1 scramblase molecules is calculated using

(y - y0)/(ymax - y0)

where y is the Relative Fluorescence Reduction and y0 is the Relative Fluorescence Reduction in an experiment without addition of protein extract. Depending on the scaleTo parameter, ymax is either the maximal Relative Fluorescence Reduction in the series (scaleTo = "data") or derived from a mono-exponential fit to the data (scaleTo = "model"). The latter (default) is a precaution for the case where the protein/phospholipid titration did not reach the plateau of the saturation curve.

A monoexponential curve is fitted unsig nlxb to either

p(≤ 1) = b - c*exp(-PPR/a)

(if forceThroughOrigin = FALSE) or

p(≤ 1) = b * (1 - exp(-PPR/a))

(if forceThroughOrigin = TRUE).

Data split apart above are recombined and a ggplot object is assembled with the following layers:

Lines (geom_line) representing the monoexponential fit(s). color is used to differentiate Experimental Series.

Segments (geom_segment) representing the PPR at which the fit constant a is equal to PPR. This tau value has the implication that at this PPR all vesicles on average have one scramblase and 63% have one or more (i.e. are active). color is used to differentiate Experimental Series.

Points (geom_point) representing the corresponding datapoints. color is used to differentiate Experimental Series.

Plots are finally facet_wraped by Experiment and labels adjusted cosmetically.-->

#Main Features
##Template Generation for Data Input
The following function generates a spreadsheet program-compatible tab-delimited 
`ASCII` template including column names, commentary, expected data type and the 
default used when ommited, supporting the user in providing the data needed.
```{r, code=formatR::usage('scramblaseAssayInputTemplate'), eval=FALSE}
```
The application agnostic tab-delimited format must be maintained for the 
completed table, which is subjected to extensive input checks when read by 
`flippant`.
